User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval

### 2013-10-04 writeups/proposal/proposal.tex
ran through style checker
Former-commit-id: 9afad637c7bdbdd16c01fce95600b9318e08e0cd [formerly 6041cf9def12b0b97b35d184794533280b64b025]
Former-commit-id: 0deebb8a2887354695f9d390255c29b0dbb98854

The StackOverflow and Twitter datasets were chosen because the human-created content between them is quite different, and I am interested in retrieval models that generalize across different task domains.
However, they are also quite similar on several accounts:
Both domains have amassed large amounts of user-created content, users generate tags for posts when creating content on the site (hashtags and tags for Twitter and StackOverflow respectively),
and the user data from the datasets are publicly available for analysis.

@@

Pointwise Mutual Information (PMI) is a another co-occurrence index that measures strength of association between two terms \parencite{Farahat2004}.
It is based on the co-occurrence count between pair-wise observations of terms, similar to ACT-R's strength of association.
The PMI index is included in Equation \eqref{eqPMI}.

@@

\textcite{Jones2007} created the BEAGLE vector-based memory representation.
Each memory vector ($m_{j}$) is a summed representation of unordered and ordered word co-occurrences ($c_{j} + o_{j}$).
This model uses circular convolution and inverse correlation as a way to encode and decode word order.
BEAGLE performed similar to LSA when trained on the TASA and tested on the TOEFL (55.6\% compared to 55.3\%).
BEAGLE with unordered context and word order was also more correlated to the WordNet synonym database than LSA (-.311 compared to -.165).
Further, it was shown that incorporating word-order information into the same representation resulted in minimal data loss (less than 1 percent of total predictive variance).
This model provided an efficient algorithm for using a single representation for unordered and ordered information that showed performance similar to if not better than LSA.

>>>>

The StackOverflow and Twitter datasets were chosen because the human-created content between them is quite different, and I am interested in retrieval models that generalize across different task domains.
However, they are also similar on several accounts:
Both domains have amassed large amounts of user-created content, users generate tags for posts when creating content on the site (hashtags and tags for Twitter and StackOverflow respectively),
and the user data from the datasets are publicly available for analysis.

@@

Pointwise Mutual Information (PMI) is another co-occurrence index that measures strength of association between two terms \parencite{Farahat2004}.
It is based on the co-occurrence count between pair-wise observations of terms, similar to ACT-R's strength of association.
The PMI index is included in Equation \eqref{eqPMI}.

@@

\textcite{Jones2007} created the BEAGLE vector-based memory representation.
Each memory vector ($m_{j}$) is a summed representation of unordered and ordered word co-occurrences ($c_{j} + o_{j}$).
This model uses circular convolution and inverse correlation as a way to encode and decode word order.
BEAGLE performed similar to LSA when trained on the TASA and tested on the TOEFL (55.6\% compared to 55.3\%).
Also, BEAGLE with unordered context and word order was more correlated to the WordNet synonym database than LSA (-.311 compared to -.165).
Further, it was shown that incorporating word-order information into the same representation resulted in minimal data loss (less than 1 percent of total predictive variance).
This model provided an efficient algorithm for using a single representation for unordered and ordered information that showed performance similar to if not better than LSA.
